\section{Discussion and Conclusion}
Overall, the \textit{Smart} algorithm appears to perform the best.
It can handle varying network topologies across different simulations, and presumably handle varying network topologies during the simulation.
There is still a vast amount of testing that can be done, but is unfortunately too large of a task to take on for this project.
I initially started my project testing switch variations that had 1 communication qubit per peer and could perform parallel BSMs,
but was unable to find any particularly interesting results or come up with any novel algorithms.
From that testing it was apparent how much more performant such a switch would be, with the maximum arrival rates before system instability
being orders of magnitude higher than the single swap algorithms I presented.
I left the parallel/multi-qubit algorithms, along with various tests and figures from those algorithms in my codebase.
\subsection{Future Work and Improvements}
To make my findings more thorough, more network topologies should be tested.
A simulation can be run that averages the performances of the algorithms on the average of every possible link length permutation within some fixed set of bounds.
I would have tried to implement this however such a test would take an excruciatingly long time to run and is why I decided not to.

As mentioned earlier, parallel BSM capable switches perform substantially better with high request rates, although I did notice they performed worse with low request rates.
It would be interesting to see if a dynamic algorithm could be implemented that selects specifically the ideal number of BSMs to make at a given moment in time, and how such and algorithm would compare.
If given more time I would want to test how different QoS policies would work, such as not discarding a lower fidelity state if the current observed load is high, for example.
It would be interesting to see how this would compare to \textit{Smart} and if there exist QoS policies that would either outperform \textit{Smart} overall or specifically work well with it.